---
title: "Market_Basket_Analysis"
author: "Ashiqur"
date: "11/2/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Load Library
```{r Library}
library(RMySQL)
library(dplyr)
library(ggplot2)
```

## Load Data
There are three table in the SQL database server.below code is the procedure to retrieve the 
table from the server
# Connecting to db
```{r Connecting_to_db}
db_user <- 'data_student_berlin'
db_password <- 'waai_has_shitty_internet'
db_name <- 'pricehub'
db_table <- 'products'
db_host <- '34.89.228.59' # for local access
db_port <- 3306

mydb <-  dbConnect(MySQL(), user = db_user, password = db_password,
                   dbname = db_name, host = db_host, port = db_port)
```
# Read data from db
```{r read_data}
s <- paste0("select * from ", db_table)
rs <- dbSendQuery(mydb, s)
products <-  fetch(rs, n = -1)
```

# Import df 'line_item'
```{r line_table}
db_table <- 'line_item'
s <- paste0("select * from ", db_table)
s <- paste0("select * from ", db_table)
rs <- dbSendQuery(mydb, s)
line_item <-  fetch(rs, n = -1)
```


# Import df 'orders'
```{r orders_table}
db_table <- 'orders'
s <- paste0("select * from ", db_table)
rs <- dbSendQuery(mydb, s)
orders <-  fetch(rs, n = -1)
```

# import df 'products'
```{r products_table}
db_table <- 'products'
s <- paste0("select * from ", db_table)
rs <- dbSendQuery(mydb, s)
products <-  fetch(rs, n = -1)
```
# Disconnect from Database 
```{r exit}
on.exit(dbDisconnect(mydb))
```

## Check for missing values
check and count how many missing value is in the table
```{r missing_value}
any(is.na(line_item))
any(is.na(orders))
any(is.na(products))


sum(is.null(line_item))
sum(is.null(products))
sum(is.null(orders))
```

##  exploring Three dataset

```{r Summarise data}
glimpse(c(line_item, orders, products))

summary(c(line_item, orders, products))

str(c(line_item, orders, products))

sum(is.na(c(line_item, orders, products)))
```

## price difference in line_item and order:
Explore the relationship between prices in line_item and order:

```{r manual_price_calculate}
head(line_item)
dim(line_item)
line_price <- line_item %>% 
        group_by(id_order) %>% 
        summarise(count_price = sum(product_quantity * unit_price))
dim(line_price)
head(line_price)
line_new<-inner_join(line_item,line_price,by="id_order")
head(line_new)
dim(line_new)
```
counting id_order which is present only in both the table and calculate the price error
```{r price_compare}

compare_total<-inner_join(line_price,orders,by="id_order")
head(compare_total)
dim(compare_total)

#mutate(compare_total,price_diff=total_paid-count_price)
compare_total$price_diff<-compare_total$count_price-compare_total$total_paid
compare_total$perc_diff <- round(((compare_total$count_price - compare_total$total_paid)/compare_total$total_paid)*100)
head(compare_total)
dim(compare_total)

```
# plot histogram 
To check the frequency of price difference 
```{r hist_price_diff}
compare_total %>% 
        filter(price_diff < 20, price_diff > -20) %>% 
        ggplot(aes(price_diff)) +
        geom_histogram()
```

## correct Value
```{r correct_price diff}
correct_price<-filter(compare_total,price_diff==0) 
head(correct_price)
dim(correct_price)
```

## in-correct Value
There is some unexpected price difference that has noticed.so only price difference (-10 to 10 )value has been considered
```{r incorrect_price diff}
incorrect_price<-filter(compare_total,price_diff!=0) 
head(incorrect_price)
dim(incorrect_price)
summary(incorrect_price)
```

## select value
price difference from  -10 to +10 has considered
```{r select}
comp_10_f<-filter(compare_total,price_diff>=(-10) & price_diff<10)
count(comp_10_f)
head(comp_10_f)
dim(comp_10_f)

# if we take percentage valu
#comp_10_f <- filter(comp_10_f, perc_diff < 10)
#comp_10_f <- filter(comp_10_f, perc_diff > -10)
```
## plot Total paid vs price difference  
```{r price_diff_plot}
#ggplot(mapping = aes(y=comp_10_f$total_paid,x=comp_10_f$price_diff))+geom_point()
comp_10_f  %>%
  ggplot(aes(x=total_paid, y=price_diff)) + 
  geom_point()
```
## suspicious value
values have not been considered 
```{r suspicious}
suspicious_df<-anti_join(line_item,comp_10_f,by="id_order")
summary(suspicious_df)
dim(suspicious_df)

```

## price difference in line_item and products:
counting sku which is present only in both the table and calculate the price error
```{r sku}
head(products)
comp_sku<-inner_join(line_item, products, by="sku")
dim(comp_sku)
head(comp_sku)
summary(comp_sku)

comp_sku$sku_p_diff=comp_sku$price- comp_sku$unit_price 
head(comp_sku)
```
# plot price difference vs price 
To check the frequency of price difference 
```{r sku_plot}
#ggplot(mapping = aes(y=comp_sku$price,x=comp_sku$sku_p_diff))+geom_jitter()

comp_sku  %>%
  ggplot(aes(x=sku_p_diff, y=price)) + 
  geom_point()
```
# plot histogram 
To check the frequency of price difference 
```{r hist_price_dif}
comp_sku %>% 
        filter(sku_p_diff < 1000, sku_p_diff > -1000) %>% 
        ggplot(aes(sku_p_diff)) +
        geom_histogram()
```

## select value
price difference from  -10 to +10 has considered
```{r select_p}
sku_1000_f<-filter(comp_sku,sku_p_diff>=(-1000) & sku_p_diff<1000)
count(sku_1000_f)
head(sku_1000_f)
```
## Correct sku value
```{r correct_sku }
correct_sku_price<-filter(comp_sku,sku_p_diff==0) 
head(correct_sku_price)
dim(correct_sku_price)
```
## In-Correct sku value
```{r incorrect_sku }
suspicious_sku<-anti_join(line_item,sku_1000_f,by="sku")
summary(suspicious_sku)
dim(suspicious_sku)
```
## crosscheck 
Check similer ID_order we deleted from both cases
```{r crosscheck}
head(suspicious_sku)
dim(suspicious_sku)
head(suspicious_df)
dim(suspicious_df)

comp_suspicious<-inner_join(suspicious_df, suspicious_sku, by="id_order")
head(comp_suspicious)
dim(comp_suspicious)
```
## Select Some specific value
only  Completed item has been chosen  in line_item table
```{r select_completed}
comp_10_f_comp <- filter(comp_10_f, state == "Completed")
dim(comp_10_f_comp)
head(comp_10_f_comp)
```
## Final table
```{r final_table}
head(line_item)
dim(line_item)

dim(line_price)
head(line_price)

#line_new<-inner_join(line_item,line_price,by="id_order")
head(line_new)

dim(comp_10_f_comp)
head(comp_10_f_comp)
dim(comp_sku)
head(comp_sku)

dim(new_Line_item_com)
head(new_Line_item_com)
dim(comp_10_f_comp)
head(comp_10_f_comp)
count(sku_1000_f)
dim(sku_1000_f)
nrow(unique(sku_1000_f))
nrow(duplicated(sku_1000_f))
head(sku_1000_f)
final_table<-comp_10_f_comp %>% 
             filter(id_order %in% sku_1000_f$id_order)
dim(final_table)
head(final_table)
nrow(unique(final_table))

final_final <- inner_join(final_table, sku_1000_f, by="id_order")
head(final_1)
dim(final_1)
nrow(unique(final_1))
nrow(duplicated(final_1))
#-------------------------------######################
new_Line_item<-inner_join(line_item,orders,by="id_order")
dim(new_Line_item)
head(new_Line_item)
dim(line_item) - dim(new_Line_item)

new_Line_item_com <- filter(new_Line_item, state == "Completed")
dim(new_Line_item_com)
head(new_Line_item_com)
(dim(line_item) - dim(new_Line_item_com))/dim(line_item)*100

new_Line_item2 <- inner_join(new_Line_item_com, products, by="sku")
dim(new_Line_item2)
head(new_Line_item2)
dim(new_Line_item_com) - dim(new_Line_item2)

# Let's transform and format the created_date column, make two new colomns Date and Time 
# and remove the created_date and date columns

new_Line_item2$Date <- as.Date(new_Line_item2$created_date)
new_Line_item2$Time <- format(as.POSIXct(new_Line_item2$created_date), format="%H:%M:%S")

new_Line_item2$date <- NULL
new_Line_item2$created_date <- NULL

dim(new_Line_item2)

# Let's remove some more unuseful columns
  
new_Line_item2 <- select(new_Line_item2, id_order, product_quantity, sku, unit_price, total_paid, name_en, short_desc_en, price, brand, manual_categories, Date, Time)

dim(new_Line_item2)
head(new_Line_item2)

final_1 <- inner_join(comp_10_f_comp, comp_sku, by="sku")
head(final_1)
dim(final_1)



```
## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
